---
title: "p8105_hw5_jdr2191"
output: github_document
---
```{r load_libraries}
library(tidyverse)
library(viridis)
```

## Problem 1

```{r}
homicide_df = 
  read_csv("./homicides/homicide-data.csv", na = c("", "Unknown")) %>%
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved"
         )) %>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")

homicide_df %>%
  count(city_state) %>% view

```

victim_age: encoded as a character (will want to address)
some other things are listed as NA

The homicide dataset contains `r count(homicide_df)` observations.

Let's look at Baltimore, MD
```{r}
baltimore_df = 
  homicide_df %>%
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n))

baltimore_test %>%
  broom::tidy()
```
64% were not solved; 95% CI of .627 to .663

Let's try to iterate across cities. 

First off, write a function
```{r}
prop_test_function = function(city_df) {

city_summary = 
  city_df %>% 
  summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
  )

city_test = 
  prop.test(x = city_summary %>% pull(unsolved), 
  n = city_summary %>% pull(n))

  return(city_test)
}

prop_test_function(baltimore_df)

homicide_df %>%
  filter(city_state == "AlbuquerqueNM") %>%
  prop_test_function()
```

Now let's iterate across cities
```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) 
```

Try to make a plot showing estimates and CIs
```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test), 
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time.
```{r create_df, message=FALSE}
files_df =
  tibble(
    participant_id = list.files("data")) 

files2_df =
  files_df %>%
  mutate(file_contents = map(participant_id , function(x) read_csv(file.path("data", x)))) %>%
  mutate(participant_id = gsub(".csv", "", participant_id)) %>%
  unnest(file_contents) %>%
  pivot_longer(
    cols = starts_with("week"),
    names_to = "week",
    names_prefix = "week_",
    values_to = "value",
  ) %>%
  separate(participant_id, c("study_arm", "subject_id"), sep = "_") %>%
  mutate(study_arm = ifelse(study_arm == "con","Control","Experimental"))
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r create_plot, message=FALSE}
files2_df %>%
  ggplot(aes(x = week, y = value)) +
  geom_line(aes(group = subject_id, color = subject_id), size = 1) +
  geom_point(aes(group = subject_id, color = subject_id)) +
  facet_grid(cols = vars(study_arm), switch = "y") + 
  scale_colour_viridis_d(option = "D") + 
  labs(x = "Week", y = "Value", col = "Subject ID") +
  theme_minimal()
```
There is less variability in values over time for the control arm than for the experimental arm. In the control arm, values seem to range from abut -2.3 to 4 whereas for the experimental arm, values seem to range from about -1 to 7.6. In the experimental arm, values for individuals apepar to increase over time throughout the course of the study.  

## Problem 3

```{r}
set.seed(10)

iris_with_missing = 
  iris %>%
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>%
  janitor::clean_names()
```

Write a function
```{r}
update_missing = function(x) {
  
   if (is.numeric(x)) {
     
     ifelse(is.na(x) == TRUE, mean(x, na.rm = TRUE), x)
     
   }
  
   else if (is.character(x)) {
    
    ifelse(is.na(x) == TRUE, "virginica", x)
    
  }

}
```

Create a new dataframe without missing values
```{r}
iris_complete = map_df(iris_with_missing, update_missing)
```

