---
title: "p8105_hw5_jdr2191"
output: github_document
---
```{r load_libraries}
library(tidyverse)
library(viridis)
```

## Problem 1
```{r, message=FALSE}
homicides_df = 
  read_csv("homicides/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")
    ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Let's focus on Baltimore MD 
```{r, message=FALSE}
baltimore_df = 
  homicides_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

balimtore_test = 
  prop.test(x = baltimore_summary %>% pull(unsolved), 
          n = baltimore_summary %>% pull(n))

balimtore_test %>% 
  broom::tidy()
```

Let's try to iterate across cities
```{r, message=FALSE}
prop_test_function = function(city_df) {

  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(x = city_summary %>% pull(unsolved), 
            n = city_summary %>% pull(n))
  
  return(city_test)
}

```

Let's iterate across all cities
```{r, message=FALSE}
results_df = 
  homicides_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Try to make a plot showing estimates and confidence intervals 
```{r, message=FALSE}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r, message=FALSE}
homicides_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test), 
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

## Problem 2

Creating a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time.
```{r create_df, message=FALSE}
files_df =
  tibble(
    participant_id = list.files("data")) 

files2_df =
  files_df %>%
  mutate(file_contents = map(participant_id , function(x) read_csv(file.path("data", x)))) %>%
  mutate(participant_id = gsub(".csv", "", participant_id)) %>%
  unnest(file_contents) %>%
  pivot_longer(
    cols = starts_with("week"),
    names_to = "week",
    names_prefix = "week_",
    values_to = "value",
  ) %>%
  separate(participant_id, c("study_arm", "subject_id"), sep = "_") %>%
  mutate(study_arm = ifelse(study_arm == "con","Control","Experimental"))
```

Making a spaghetti plot showing observations on each subject over time, and commenting on differences between groups.
```{r create_plot, message=FALSE}
files2_df %>%
  ggplot(aes(x = week, y = value)) +
  geom_line(aes(group = subject_id, color = subject_id), size = 1) +
  geom_point(aes(group = subject_id, color = subject_id)) +
  facet_grid(cols = vars(study_arm), switch = "y") + 
  scale_colour_viridis_d(option = "D") + 
  labs(x = "Week", y = "Value", col = "Subject ID") +
  theme_minimal()
```
There is less variability in values over time for subjects in the control arm than for subjects in the experimental arm. In the control arm, values for individuals range from about -2.3 to 4 whereas for the experimental arm, values range from about -1 to 7.6. In the control arm, although values fluctuate for individuals over the 8 weeks of the study, there is no clear linear pattern in how they fluctuate from Week 1 to Week 8. On the other hand, values for individuals in the experimental arm generally increase over time throughout the course of the study in a way that is roughly linear. 

## Problem 3

Loading the iris dataset from the tidyverse package and introducing some missing values in each column.
```{r import_data, message=FALSE}
set.seed(10)

iris_with_missing = 
  iris %>%
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>%
  janitor::clean_names()
```

Writing a function that takes a vector as an argument and replaces missing values so that:

* Missing values for numeric variables are replaced with the mean of non-missing values

* Missing values for character variables are replaced with "virginica"

This function will then return the resulting vector. 
```{r function, message=FALSE}
update_missing = function(x) {
  
   if (is.numeric(x)) {
     
     ifelse(is.na(x) == TRUE, mean(x, na.rm = TRUE), x)
     
   }
  
   else if (is.character(x)) {
    
    ifelse(is.na(x) == TRUE, "virginica", x)
    
  }

}
```

Applying this function to the columns of iris_with_missing using a map statement.
```{r replace_missing, message = FALSE}
iris_complete = 
  map_df(iris_with_missing, update_missing)
```

